### 2016-09-21 doc/manuscript.Rmd
(very) rough draft of discussion

- Run PLS with just those FA that loaded strongly to see the predictive ability.
- SA with/without NEFA
- SA with/without WC

@@

>>>>

- Run PLS with just those FA that loaded strongly to see the predictive ability.
- SA with/without NEFA
- SA with/without WC
- Interactions of VN unadjusted

@@

We found that in a Canadian population of mainly female and European ancestry, 
the specific TAGFA composition was strongly associated with insulin sensitivity
and moderately associated with beta-cell function. In particular, TAGFA myristic 
acid (14:0), 7-tetradecenoic acid {{ confirm }} (14:1n-7), palmitic acid (16:0),
and palmitoleic acid (16:1n-7) all strongly and negatively predicted lower
insulin sensitivity. While

Limitations:
- While GEE is well suited to longitudinal datasets.. threre is a possibility
given teh complex biology that the temporal associations can not be adequately
analyzed using current methodologies. IN particular, an important issue si taht
we did not quantify TAGFA at each of the three visits and so can not directed
infer changes in TAGFA with changes in IR. However, given potential feedback
between IR and TAGFA, this may in fact be a strength for this particular
association given we are trying to predict how a FA at one time point can
predict future values.
- While PLS is a well-established technique for constructing predictive models
of high dimensionality data strcutures, it can not adjust for potential
confounders and other effect modifiers. Likewise, PLS is not able to handle
longitudinal data so only the baseline visit was used in the PLS analysis.
However, given the limitation, there results are concordant between GEE and PLS
models.
- Our population was predocminiately female and of euro ancestry, who were at 
riskj for diabetes at study enrollment, and as such our results may not be
generalizable to other populations.
- Given the complex biology underlying the variables of interest, there many
some residual confounding we are unaware of or have not been able to adjust for.
However, we have taken extensive precautions for trying to ID confounders
through the DAG models and QIC computations.

Interpretation:

- previous research has shown that CHO intake increases DNL {{ cite }}. In
particular, DNL from CHO sources increases especially the 14-16 chain TAGFA as
well as the 18 chain TAGFA. Prev lit has also shown that higher DNL can increase
risk for DM {{ cite }} and that higher refined CHO can increase risk of DM {{
cite }}. Our study found that the 14-16 TAGFA all strongly predicted lower
insulin sensitivity, reinforcing this finding. While these FA also had a
significant association with beta-cell function, the results were not as strong
as with the IR. {{ why is it that DNL increases risk? }}
- TAGFA that tended to positively associated with IR and BCF also tended to be
the very long chain FA such as eicosapentaenoic acid (20:5n-3) and
docosahexaenoic acid (22:6n-3), which have potent anti-inflammatory properties
{{ cite }}. Biologically {{ why these FA and how help with IR }}
- {{ compare models with and without NEFA }} NEFA have been shown contribute
substantially to TAGFA composition and concentration. Adjusting for ...
- Dietary FA have been shown to contribute approx 25% of the newly synth
VLDL-TAG {{ cite }}. This suggests that our results may not entirely reflect
diet, but also adipose stores. {{ discuss results of NEFA paper }} However, in
an analysis of the NEFA pool {{ cite }}, we found that total NEFA, but not the
specific composition associated with beta-cell function. There may be something
unique about the specific composition of the TAGFA fraction that may allow it to
enter IR tissues more easily than NEFA. It may be that VLDL receptors allow FA
to transition to IR tissue compared to NEFA bound to albumin {{ confirm and cite
}}.

Previous lit and limits:

-

New things:

- No longitudinal study has examined all these TAGFA using detailed metabolic,
OGTT-derived measures. No study has used these statistical techniques, which
were designed with these types of data in mind, and as such allows appropriate
conclusions to be reached from this data.
- That 14-16 FA in the TAGFA fraction predict lower insulin sensitivity and that
this particular cluster is also generally observed with higher CHO intake.
